### 2022-11-08 NSF2022/Description/priorsupport.tex
removed extra commas in bibtex

\noindent
{\it Broader impacts:} 
A third-year PhD student (Jake Cherry) has been assigned to this
project. One paper will be submitted before December
2021~\cite{lin-her-qua-che2021}.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be RR
  (red), BQ (blue), and YNY (green). Project management will be
  continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms,
and computing. PI RR has been working on mathematical modeling with a
strong analytical background. PI YNY has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. PI BQ has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two
dimensions~\cite{FuQuRyYo20} has provided a solid foundation for the
proposed research.

>>>>

\noindent
{\it Broader impacts:} 
A third-year PhD student (Jake Cherry) has been assigned to this
project. One paper will be submitted before December
2021~\cite{che-lin-her-qua2022}.

@@

\begin{comment}
\begin{wrapfigure}[11]{r}{0.56\textwidth}
\vspace{-19pt}
%\definecolor{barblue}{RGB}{51,102,254}
%\renewcommand\sfdefault{phv}
%\renewcommand\mddefault{mc}
%\renewcommand\bfdefault{bc}
%\sffamily
\begin{ganttchart}[
    canvas/.append style={fill=none, draw=black!5, line width=.75pt},
        x unit =4.5mm,
        y unit chart =\baselineskip,
    hgrid style/.style={draw=black!5, line width=.75pt},
    vgrid={*1{draw=black!5, line width=.75pt}},
    title/.style={draw=none, fill=none},
    title label font=\bfseries\footnotesize, % numbers across the top
    title label node/.append style={below=3pt},
    include title in canvas=false,
    bar label font=\mdseries\footnotesize\color{black!70}, 
    % titles across the left
    %bar label node/.append style={left=2cm},
    bar/.append style={draw=none, fill=blue},
    bar incomplete/.append style={fill=blue},
    bar progress label font=\mdseries\footnotesize\color{black!70},
    milestone label font=\mdseries\small\color{black!70},
        milestone left shift =0.9,
        milestone right shift =0.1,
        % Don't draw group bars
        group height =0,
        group peaks height =0,
        group label font =\bfseries\small,
]{1}{12}
\gantttitle[
    title label node/.append style={below left=3pt and -6pt}
]{QUARTERS:\quad1}{1}
\gantttitlelist{2,...,12}{1} \\
%\ganttgroup{Tasks\hfill}{1}{12}\\
\ganttbar[bar/.append style={fill=red}]{Specific Aim 1}{1}{12} \\
\ganttbar[bar/.append style={fill=blue}]{Specific Aim 2}{1}{12}\\
\ganttbar[bar/.append style={fill=green}]{Specific Aim 3}{1}{12}\\
\ganttbar[bar/.append style={fill=black}]{Program Management}{1}{12}
\ganttbar[bar/.append style={fill=magenta}]{}{4}{4}
\ganttbar[bar/.append style={fill=magenta}]{}{8}{8}
\ganttbar[bar/.append style={fill=magenta}]{}{12}{12}
\end{ganttchart}
\vspace{-10pt}
\caption{Schedule for the proposed work, measured in quarters from the
  beginning of the project. The lead PI of each Specific Aim will be RR
  (red), BQ (blue), and YNY (green). Project management will be
  continuous (black), but we anticipate extra attention will be
  necessary to align objectives in quarters 4, 8, and 12 (magenta).}
\label{fig:schedule}
\end{wrapfigure}
\end{comment}
\textbf{Project management}: 
%
The success of the proposed research requires complementary expertise
and collaborative efforts in physics, applied mathematics, algorithms,
and computing. PI RR has been working on mathematical modeling with a
strong analytical background. PI YNY has been working on many areas of
computational fluid dynamics and applications to math biology for many
years. PI BQ has been working on integral equation methods, fast
algorithms, and their applications to fluid dynamics for many years.
Their recent collaborative work on the HAP model in two
dimensions~\cite{FuQuRyYo22} has provided a solid foundation for the
proposed research.

### 2022-11-08 NSF2022/Description/specificaim2.tex
removed extra commas in bibtex

%\label{subsec:specific_aim_2}
%\begin{wrapfigure}[14]{r}{0.61\textwidth}
%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
%    \vspace{-15pt}
%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
%    amphiphilic particles suspended in a solvent. The solvent velocity
%    satisfies the Stokes equations, and the hydrophobic forces depend on
%    the solvent activity that satisfies the screened Laplace equation.
%    The geometry is updated by solving the mobility problem.} 
%\end{wrapfigure}
The HAP model requires solving exterior problems for the order
parameter~\eqref{eqn:phase} and the Stokes equations~\eqref{eqn:stokes}.
We will develop methods based on combinations of volume and layer
potentials, and inexact Newton's method. As mentioned in
Section~\ref{sec:bie}, numerical methods to solve these integral
equations (IEs) have several advantages over their PDE-based
counterpart. The PIs have demonstrated that IEs are a powerful tool to
simulate two-dimensional suspensions of amphiphilic
particles~\cite{Fu2018_SIAM, FuQuRyYo20, fu-ryh-qua-you2022}. Moreover,
elements of these formulations have been described in three
dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
will extend the two-dimensional methods to more general amphiphilic
particle models and also to three dimensions. In addition, the methods
will allow us to use results we have shown for $\mathcal{O}(100)$
grains, and extend them to suspensions with 100X--1000X more grains.
These methods will be motivated by models and analysis developed in
Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the non-linear
Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using an IE
formulation. Then, \S\ref{subsec:NumericalIssues} describes how we will
combine accurate quadrature and fast summation methods to accelerate the
time to accurate solutions. A natural extension to create simulations
that are realizable by experimentalists is to include confinement, and
this is discussed in \S\ref{subsec:Confinement}. This extension will
also allow us to study new rheological properties of the suspensions.
Finally, \S\ref{subsec:timeStepping} proposes collision-aware adaptive
time stepping methods.

@@

In two-dimensions, analytic function theory can be used to derive a
quadrature method whose error is uniformly bounded~\cite{bar2014,
bar-wu-vee2015, ioa-pap-per1991}, but these works only show how to apply
the method to the two-dimensional Laplace and Stokes equations. PI BQ
recently showed that these quadrature methods can be extended to other
PDEs with singularity subtraction~\cite{che-lin-her-qua2021}. For
example, the fundamental solution of the screened Laplace
equation~\eqref{eqn:phase} involves the modified Bessel function of the
second kind, $K_0(\|\xx - \yy\|)$. The behavior of this function as $\yy
\rightarrow \xx$ is $K_0(\alpha \|\xx - \yy\|) = \log\|\xx - \yy\| +
S(\xx - \yy)$, where $S(\xx - \yy)$ is continuously differentiable. This
suggests a quadrature scheme for where the aforementioned quadrature
method is applied to the $\log\|\xx - \yy\|$ kernel, and high-order
methods~\cite{tre-wei2014} are applied to integrals involving the smooth
kernel $S(\xx - \yy)$.Similar techniques, which they call subtraction
techniques, have been considered by Camille Carvalho and her
colleagues~\cite{car2021, car2020, car-kha-kim2018}.  These methods are
particularly powerful when computing gradients of layer potentials which
is required, for example, when computing the water-order
stress~\eqref{eqn:stressbalance}.

>>>>

%\label{subsec:specific_aim_2}
%\begin{wrapfigure}[14]{r}{0.61\textwidth}
%  \centering{\includegraphics[width=0.60\textwidth]{Figures/domain.pdf}}
%    \vspace{-15pt}
%    \caption{\label{fig:flow_map} \footnotesize A collection of 3D
%    amphiphilic particles suspended in a solvent. The solvent velocity
%    satisfies the Stokes equations, and the hydrophobic forces depend on
%    the solvent activity that satisfies the screened Laplace equation.
%    The geometry is updated by solving the mobility problem.} 
%\end{wrapfigure}
The HAP model requires solving exterior problems for the order
parameter~\eqref{eqn:phase} and the Stokes equations~\eqref{eqn:stokes}.
We will develop methods based on combinations of volume and layer
potentials, and inexact Newton's method. As mentioned in
Section~\ref{sec:bie}, numerical methods to solve these integral
equations (IEs) have several advantages over their PDE-based
counterpart. The PIs have demonstrated that IEs are a powerful tool to
simulate two-dimensional suspensions of amphiphilic
particles~\cite{Fu2018_SIAM, FuQuRyYo22, fu-ryh-qua-you2022}. Moreover,
elements of these formulations have been described in three
dimensions~\cite{ying_2006, manasthesis, rac-gre2016}. This proposal
will extend the two-dimensional methods to more general amphiphilic
particle models and also to three dimensions. In addition, the methods
will allow us to use results we have shown for $\mathcal{O}(100)$
grains, and extend them to suspensions with 100X--1000X more grains.
These methods will be motivated by models and analysis developed in
Specific Aims 1 and 3. \S\ref{subsec:AC} describes how the non-linear
Allen-Cahn equation~\eqref{eq:SL} will be iteratively solved using an IE
formulation. Then, \S\ref{subsec:NumericalIssues} describes how we will
combine accurate quadrature and fast summation methods to accelerate the
time to accurate solutions. A natural extension to create simulations
that are realizable by experimentalists is to include confinement, and
this is discussed in \S\ref{subsec:Confinement}. This extension will
also allow us to study new rheological properties of the suspensions.
Finally, \S\ref{subsec:timeStepping} proposes collision-aware adaptive
time stepping methods.

@@

In two-dimensions, analytic function theory can be used to derive a
quadrature method whose error is uniformly bounded~\cite{bar2014,
bar-wu-vee2015, ioa-pap-per1991}, but these works only show how to apply
the method to the two-dimensional Laplace and Stokes equations. PI BQ
recently showed that these quadrature methods can be extended to other
PDEs with singularity subtraction~\cite{che-lin-her-qua2022}. For
example, the fundamental solution of the screened Laplace
equation~\eqref{eqn:phase} involves the modified Bessel function of the
second kind, $K_0(\|\xx - \yy\|)$. The behavior of this function as $\yy
\rightarrow \xx$ is $K_0(\alpha \|\xx - \yy\|) = \log\|\xx - \yy\| +
S(\xx - \yy)$, where $S(\xx - \yy)$ is continuously differentiable. This
suggests a quadrature scheme for where the aforementioned quadrature
method is applied to the $\log\|\xx - \yy\|$ kernel, and high-order
methods~\cite{tre-wei2014} are applied to integrals involving the smooth
kernel $S(\xx - \yy)$.Similar techniques, which they call subtraction
techniques, have been considered by Camille Carvalho and her
colleagues~\cite{car2021, car2020, car-kha-kim2018}.  These methods are
particularly powerful when computing gradients of layer potentials which
is required, for example, when computing the water-order
stress~\eqref{eqn:stressbalance}.
